# Anscombe's Quartet

You may be asking now, why bother visualizing data if I have all these numbers that will tell me what I need to know about my data? You are correct in saying that statistical data is very useful, and in many cases essential, however visualization is equally as important. Anscombe's Quartet is a statistical phenomenon where four sets of data have very similar statistical properties, but very are completely different when graphed. Let's take a look at the data:

```{r, echo=FALSE,warning=FALSE,error=FALSE,message=FALSE}
library(fBasics)
library(ggplot2)
library(grid)
library(gridExtra)
library(datasets)
datasets::anscombe
```

```{r,echo=FALSE,include=TRUE,warning=FALSE,error=FALSE,message=FALSE}

fBasics::basicStats(anscombe)
```

As you can see from the table, the summary statistics for the four tables look very similar, however let's graph these and see what kind of visualizations we get.

```{r,echo=FALSE,warning=FALSE,error=FALSE,message=FALSE}
p1 <- ggplot(anscombe) +
  geom_point(aes(x1, y1), color = "darkorange", size = 1.5) +
  scale_x_continuous(breaks = seq(0,20,2)) +
  scale_y_continuous(breaks = seq(0,12,2)) +
  expand_limits(x = 0, y = 0) +
  labs(x = "x1", y = "y1",
       title = "Dataset 1" ) +
  theme_bw()

p2 <- ggplot(anscombe) +
  geom_point(aes(x2, y2), color = "darkorange", size = 1.5) +
  scale_x_continuous(breaks = seq(0,20,2)) +
  scale_y_continuous(breaks = seq(0,12,2)) +
  expand_limits(x = 0, y = 0) +
  labs(x = "x2", y = "y2",
       title = "Dataset 2" ) +
  theme_bw()

p3 <- ggplot(anscombe) +
  geom_point(aes(x3, y3), color = "darkorange", size = 1.5) +
  scale_x_continuous(breaks = seq(0,20,2)) +
  scale_y_continuous(breaks = seq(0,12,2)) +
  expand_limits(x = 0, y = 0) +
  labs(x = "x3", y = "y3",
       title = "Dataset 3" ) +
  theme_bw()

p4 <- ggplot(anscombe) +
  geom_point(aes(x4, y4), color = "darkorange", size = 1.5) +
  scale_x_continuous(breaks = seq(0,20,2)) +
  scale_y_continuous(breaks = seq(0,12,2)) +
  expand_limits(x = 0, y = 0) +
  labs(x = "x4", y = "y4",
       title = "Dataset 4" ) +
  theme_bw()
```

```{r,echo=FALSE,include=TRUE,warning=FALSE,error=FALSE,message=FALSE}
grid.arrange(grobs = list(p1, p2, p3, p4), 
             ncol = 2, 
             top = "Anscombe's Quartet")
```

Pretty rad right? So yes, statistical data is vital, however it should not be the only thing you look at, sometimes a visualization can help you understand the data more! Later in this book, and in the upper level data analytics courses, we will cover visualizations more and how they can be useful.